---
title: "Overview Map"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:
```{r}
library(leaflet)
library(mapview)
library(sf)
library(dplyr)
```

```{r}
wd=getwd()

files1="C:/Users/oc3512/Documents/ArcGIS/Projects/MMSP/MMSP.gdb"
files2="C:/Users/oc3512/Documents/ArcGIS/Projects/MMSP/MMSP(20181005).gdb"

# Check layers in the gdb
layers1=st_layers(files1)
layers2=st_layers(files2)

# Read stations and main lines
stations=st_read(files2,layers2$name[1])
ml=st_read(files2,layers2$name[2])
depot=st_read(files2,layers2$name[4])
ml_noZ=st_zm(ml,drop=TRUE,what="ZM")
ML=as(ml_noZ,"Spatial")

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
#####################
### use "leaflet"####
#####################

## Collect providers
esri <- grep("^Esri", providers, value = TRUE)
esri=c(esri,"MtbMap","Stamen.TonerLines","Stamen.TonerLabels")

## Base codes
TEST=leaflet() %>% 
  addAwesomeMarkers(data=stations,label=~as.character(stations$Name),group="Stations",
                    labelOptions=labelOptions(noHide=TRUE,textOnly=TRUE)) %>%
  addScaleBar(position="bottomleft") %>%
  addMiniMap(tiles=esri[[1]],zoomLevelOffset = -5,toggleDisplay = TRUE, position="bottomright") %>%
  addPolylines(data=ML,group="Main Line")

## Add each provider map to TEST
for (provider in esri) {
  if(provider=="Stamen.TonerLines"){
    TEST <- TEST %>% addProviderTiles(provider,group=provider,options=providerTileOptions(opacity=0.25))
  } else {
    TEST <- TEST %>% addProviderTiles(provider, group = provider)  
  }
}

## Final map
TEST %>%
  setView(121.07,14.61,zoom=12) %>%
  addLayersControl(baseGroups = names(esri),options = layersControlOptions(collapsed = TRUE),
                   overlayGroups = c("Stations", "Main Line"))
  htmlwidgets::onRender("
    function(el, x) {
      var myMap = this;
      myMap.on('baselayerchange',
        function (e) {
          myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
        })
    }")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r,echo=FALSE}
#####################  
### Use "mapview" ###
#####################

stNames=unique(stations$Name)
depot$Contract="CP101"

MMSP=stations %>% mutate(Contract=factor(ifelse(stNames %in% stNames[1:3],"CP101",
                                           ifelse(stNames %in% stNames[4:8],"CP102",
                                                  ifelse(stNames %in% stNames[9:16],"CP103","CP109"))))) %>%
  mapview(zcol="Contract",burst=TRUE,layer.name="Stations") + 
  mapview(depot,zcol="Contract",burst=TRUE,layer.name="Depot (CP101)") +
  mapview(ml,color="red",lwd=0.5,layer.name="Main Line")
```

